Assessment of the KLGO Coastal Waterbird Survey Monitoring Program

### 2019-04-19 analysis/paper/paper.Rmd
occurrence_freq still in progress but I have a better idea; small changes to data_wrangling to accommodate surveys w/o sightings; changed survey_dates to your recommendations & adapted into paper.Rmd

```{r SurveyDates, eval=TRUE, cache = FALSE, include = FALSE}
# scatterplot of species' first and last sightings
source("../scripts/survey_dates.R", echo=FALSE)
```

@@

```{r Fig-SurveyDates2, echo=FALSE, eval=TRUE, cache=TRUE, fig.show= 'asis', fig.cap="The last sighting of each species each year."}
print(plot_timing_2)
```

>>>>

```{r SurveyDates, eval=TRUE, cache = FALSE, include = FALSE}
# scatterplot of species' first and sightings compared to survey season start
source("../scripts/survey_dates.R", echo=FALSE)
```

@@

#to do
